Postural developments mediate children's visual access to social information

### 2018-01-25 writeup-cogsci/cogsci2018_faceOnly.Rmd
fixed plots and glm details

## EVALUATE FACE DETECTORS
performanceFaces <- ground_truth_faces  %>%
  mutate(frame=as.numeric(frame), subid=video) %>%
  left_join(dlong)   %>%
  filter(detectorType!="OpenPose-Wrists") %>%
  mutate(detector_is_face = detection, is_face = as.logical(is_face)) %>%
  rowwise() %>%
  mutate(result = evaluate(is_face, detector_is_face)) %>%
  group_by(detectorType, sample_type) %>%
  summarise(tp=sum(result == "TP"), fp=sum(result == "FP"), fn=sum(result=="FN")) %>%
  group_by(detectorType, sample_type) %>%
  summarise(p = tp / (tp + fp), r = tp / (tp + fn), f=( 2 * p * r )/ (p + r)) %>%
  xtable %>%
  print(digits = 2, include.rownames=FALSE,table.placement = "H", type="latex", comment = F)

## EVALUATE WRIST DETECTOR
performanceWrists <- ground_truth_wrists  %>%
  mutate(frame=as.numeric(frame), subid=video) %>%
  left_join(dlong)   %>%
  filter(detectorType=="OpenPose-Wrists") %>%
  mutate(detector_is_wrist = detection, is_wrist = as.logical(is_face)) %>%
  rowwise() %>%
  mutate(result = evaluate(is_wrist, detector_is_wrist)) %>%
  group_by(detectorType, sample_type) %>%
  summarise(tp=sum(result == "TP"), fp=sum(result == "FP"), fn=sum(result=="FN")) %>%
  group_by(detectorType, sample_type) %>%
  summarise(p = tp / (tp + fp), r = tp / (tp + fn), f=( 2 * p * r )/ (p + r)) %>%
  xtable %>%
  print(digits = 2, include.rownames=FALSE,table.placement = "H", type="latex", comment = F)

@@

```{r echo=FALSE, include=FALSE}

## First try a normal logistic regressino, grouping by subject / posture / orientation
# wrangle data
dModelGLM <- d %>%
  group_by(subid, posture, orientation) %>%
  summarize(countDetected=sum(faceMT==TRUE), countTotal = sum(faceMT==FALSE), age.at.test=age.at.test[1])
y=cbind(dModelGLM$countDetected, dModelGLM$countTotal) # successes / failures for modeling proportions
dModelGLM$age.at.test=scale(dModelGLM$age.at.test) # scale and center continous predictor
# run model
normalGLM<-glm(y ~ dModelGLM$age.at.test + dModelGLM$posture + dModelGLM$orientation,family=binomial(logit))
# output results
normalGLM <- normalGLM %>%
  xtable %>%
  print(type="latex", comment = F, table.placement = "H")

# Then fit a mixed effet model
fullModel <- glmer(faceMT ~ scale(age.at.test)+(posture)+(orientation) + (1|subid),
       data = d,
       family = "binomial")

# Fails to converge
# fullModel <- glmer(is_face ~ scale(age.at.test)*(posture) *(orientation) + (1|subid),
#       data = d,
#       family = "binomial")

# Fails to converge
# agexOrientation <- glmer(faceNum ~ scale(age.at.test) * orientation + (1|subid),
#       data = d,
#       family = "binomial")

fullModelminsInt_Faces_MTCNN <- glmer(faceNum_MT ~ scale(age.at.test) + posture + orientation + (1|subid),
       data = d,
       family = "binomial")

 <- glm(faceNum_MT ~ scale(age.at.test) + posture + orientation,
       data = d,
       family = "binomial")

## Check for singularity
fm1=fullModelminsInt_Faces_MTCNN
diag.vals <- getME(fm1,"theta")[getME(fm1,"lower") == 0]
any(diag.vals < 1e-6) # FALSE

source(system.file("utils", "allFit.R", package="lme4"))
fm1.all <- allFit(fm1)
ss <- summary(fm1.all)

ageOnly_MTCNN <- glmer(faceNum_MT ~ scale(age.at.test) + (1|subid),
       data = d,
       family = "binomial")

fullModelminsInt_Faces_OP <- glmer(faceNum_OP ~ scale(age.at.test) + posture + orientation + (1|subid),
       data = d,
       family = "binomial")

## try plain logistic regression
## think about classification techniques -- ?

@@

@@

\begin{table}[H]
\centering
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\
  \hline
(Intercept) & -4.846 & 0.077 & -62.682 & 0.000 \\
  Age & 0.170 & 0.061 & 2.766 & 0.006 \\
  Posture-Prone & -0.513 & 0.036 & -14.045 & 0.000 \\
  Posture-Sit & 0.648 & 0.034 & 18.853 & 0.000 \\
  Posture-Stand & 1.005 & 0.035 & 28.402 & 0.000 \\
  Orient.-Close & 1.549 & 0.021 & 72.757 & 0.000 \\
  Orient.-Far & 2.258 & 0.022 & 101.138 & 0.000 \\
   \hline
\end{tabular}
\caption{Results from GLMM model predicting the presence/absence of a face across the entire dataset (MTCNN detectors).}
\end{table}

@@

p1=ggplot(aroundNamings_subAvg_Posture, aes(x = posture, y = mean, col = posture)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) +
  ylab("Prop. faces detected") +
  xlab("") +
  theme_few() + 
  theme(legend.position="none")

p2=ggplot(aroundNamings_subAvg_Orient, aes(x = orientation, y = mean, col = orientation)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) +
  ylab("Prop. faces detected") +
  xlab("") +
  theme_few() +
  theme(legend.position="none")

@@

```{r session_info, include=FALSE, echo=FALSE}
devtools::session_info()
```

>>>>

## EVALUATE FACE DETECTORS
performanceFaces <- ground_truth_faces  %>%
  mutate(frame=as.numeric(frame), subid=video) %>%
  left_join(dlong)   %>%
  filter(detectorType!="OpenPose-Wrists") %>%
  mutate(detector_is_face = detection, is_face = as.logical(is_face)) %>%
  rowwise() %>%
  mutate(result = evaluate(is_face, detector_is_face)) %>%
  group_by(detectorType, sample_type) %>%
  summarise(tp=sum(result == "TP"), fp=sum(result == "FP"), fn=sum(result=="FN")) %>%
  group_by(detectorType, sample_type) %>%
  summarise(p = tp / (tp + fp), r = tp / (tp + fn), f=( 2 * p * r )/ (p + r)) 
  # xtable %>%
  # print(digits = 2, include.rownames=FALSE,table.placement = "H", type="latex", comment = F)

## EVALUATE WRIST DETECTOR
performanceWrists <- ground_truth_wrists  %>%
  mutate(frame=as.numeric(frame), subid=video) %>%
  left_join(dlong) %>%
  filter(detectorType=="OpenPose-Wrists") %>%
  mutate(detector_is_wrist = detection, is_wrist = as.logical(is_face)) %>%
  rowwise() %>%
  mutate(result = evaluate(is_wrist, detector_is_wrist)) %>%
  group_by(detectorType, sample_type) %>%
  summarise(tp=sum(result == "TP"), fp=sum(result == "FP"), fn=sum(result=="FN")) %>%
  group_by(detectorType, sample_type) %>%
  summarise(p = tp / (tp + fp), r = tp / (tp + fn), f=( 2 * p * r )/ (p + r)) 
  # xtable %>%
  # print(digits = 2, include.rownames=FALSE,table.placement = "H", type="latex", comment = F)

@@

```{r echo=FALSE, include=FALSE}
# First try a normal logistic regressino, grouping by subject / posture / orientation
#wrangle data
dGLM_faces <- d %>%
  group_by(subid, posture, orientation) %>%
  summarize(countDetected_Faces=sum(faceMT==TRUE), countTotal_Frames = sum(faceMT==FALSE), age.at.test=age.at.test[1])

dGLM_wrists <- d %>%
  group_by(subid, posture, orientation) %>%
  summarize(countDetected_Wrists=sum(wristOP==TRUE), countTotal_Frames = sum(wristOP==FALSE),   age.at.test=age.at.test[1])

# scale cont predictors
dGLM_faces$age.at.test=scale(dGLM_faces$age.at.test)
dGLM_wrists$age.at.test=scale(dGLM_wrists$age.at.test)

# successes / failures data structure for glm
y_faces=cbind(dGLM_faces$countDetected_Faces, dGLM_faces$countTotal_Frames)  
y_wrists=cbind(dGLM_wrists$countDetected_Wrists, dGLM_wrists$countTotal_Frames)

# run models
glm_faces<-glm(y_faces ~ dGLM_faces$age.at.test * dGLM_faces$posture * dGLM_faces$orientation,family=binomial(logit))
xtable(summary(glm_faces))

glm_wrists<-glm(y_wrists ~ dGLM_wrists$age.at.test * dGLM_wrists$posture * dGLM_wrists$orientation,family=binomial(logit))

## OUTPUT GLM RESULTS
cleanedNames = c("Intercept","Age","Prone","Sit","Stand","Close","Far", "Age:Prone","Age:Sit","Age:Stand","Age:Close",
          "Age:Far","Prone:Close","Sit:Close","Stand:Close","Prone:Far","Sit:Far","Stand:Far","Age:Prone:Close",
          "Age:Sit:Close","Age:Prone:Far","Age:Sit:Far")
faceGLMOut=xtable(summary(glm_faces))
rownames(faceGLMOut)<-cleanedNames

wristGLMOut=xtable(summary(glm_wrists))
rownames(wristGLMOut)<-cleanedNames

@@

```{r results="asis"}
print(faceGLMOut, type="latex", comment = F, table.placement = "H")
print(wristGLMOut, type="latex", comment = F, table.placement = "H")
```

<!-- # # output results -->
<!-- normalGLM <- normalGLM %>% -->
<!--   xtable %>% -->
<!--   print(type="latex", comment = F, table.placement = "H") -->

<!-- # ## Then try a run mixed effet model -->
<!-- # ## Interactions fail to converge, as does the one below -->
<!-- # fullModelminsInt_Faces_MTCNN <- glmer(faceMT ~ scale(age.at.test)+(posture)+(orientation) + (1|subid), -->
<!-- #        data = d, -->
<!-- #        family = "binomial") -->

<!-- ## Reading https://rdrr.io/cran/lme4/man/convergence.html -->
<!-- ## Check for singularity - not an issue -->
<!-- # fm1=fullModelminsInt_Faces_MTCNN -->
<!-- # diag.vals <- getME(fm1,"theta")[getME(fm1,"lower") == 0] -->
<!-- # any(diag.vals < 1e-6) # FALSE -->

<!-- ## But has issues with every optimizer... -->
<!-- #source(system.file("utils", "allFit.R", package="lme4")) -->
<!-- #fm1.all <- allFit(fm1) -->
<!-- #ss <- summary(fm1.all) -->

<!-- #No convergence issues with open pose detectors -->
<!-- fullModelminsInt_Faces_OP <- glmer(faceOP ~ scale(age.at.test) + posture + orientation + (1|subid), -->
<!--        data = d, -->
<!--        family = "binomial") -->

<!-- fullModelminsInt_Wrist_OP <- glmer(wristOP ~ scale(age.at.test) + posture + orientation + (1|subid), -->
<!--        data = d, -->
<!--        family = "binomial") -->
<!-- ``` -->

@@

@@

p1=ggplot(aroundNamings_subAvg_Posture, aes(x = posture, y = mean, col = posture)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) +
  ylab("Prop. faces") +
  xlab("") +
  ylim(0,.3) +
  theme_few() + 
  theme(legend.position="none")

p2=ggplot(aroundNamings_subAvg_Orient, aes(x = orientation, y = mean, col = orientation)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) +
  ylab("Prop. faces") +
  xlab("") +
  ylim(0,.3) +
  theme_few() +
  theme(legend.position="none")

@@

# ```{r session_info, include=FALSE, echo=FALSE}
# devtools::session_info()
# ```
